In mammals, 20 to 40\% of advantageous mutations are restoring damaged genomes instead of creating adaptive innovations

### 2022-07-08 manuscript/include-MutSel-non-adaptive.tex
D. Hartasanchez corrections. Epistasis discussion. Removed Canis Lupus (too much div to sister species).

\subsection{All populations}
\begin{center}
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.all.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-strong.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-weak.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos-weak.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos.stacked.pdf}

\end{center}

@@

\subsubsection{Iran (IRBT)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.IRBT.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.IRBT.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Uganda (UGBT)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.UGBT.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.UGBT.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Canis familiaris}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Canis_familiaris.dogs.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Canis_familiaris.dogs.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\subsubsection{Australia (AUCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.AUCH.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.AUCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{France (FRCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.FRCH.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.FRCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IRCA) - Capra aegagrus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCA.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCA.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IRCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCH.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Italy (ITCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.ITCH.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.ITCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Morocco (MOCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.MOCH.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.MOCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Barbados.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Central African Republic (CAR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Central_African_Republic.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Ethiopia.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Gambia.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Kenya.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Nevis.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Saint Kitts (SK)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Saint_Kitts.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{South Africa (SA)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.South_Africa.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\subsubsection{African (AFR)}

>>>>

\subsection{All populations}
\begin{center}
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.all.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-strong.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-weak.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos-weak.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos.stacked.pdf}
\end{center}

@@

\subsubsection{Iran}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.IRBT.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.IRBT.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Uganda}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.UGBT.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.UGBT.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\subsubsection{Australia}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.AUCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.AUCH.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{France}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.FRCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.FRCH.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (C. aegagrus)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCA.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCA.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCH.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Italy}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.ITCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.ITCH.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Morocco}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.MOCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.MOCH.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Barbados.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Central Afr. Rep.}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Central_African_Republic.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Ethiopia.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Gambia.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Kenya.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Nevis.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Saint Kitts}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Saint_Kitts.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{South Africa}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.South_Africa.MutSel.histogram.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

@@

\subsubsection{African}
